---
bibliography: biblio.bib
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# SemiCompRisksFreq

<!-- badges: start -->
<!-- badges: end -->

The goal of SemiCompRisksFreq is to fit parametric fraity-based illness-death models for analyzing semi-competing risks data. This package is meant as a development extension of the
SemiCompRisks package found on CRAN; whereas that package focuses on Bayesian estimation
of various illness-death models, this package focuses on frequentist estimation, with
a variety of additional features implemented for summary and prediction. For more information, these methods have been examined and demonstrated in [@reeder2019joint], [@reeder2022methods], [@reeder2023novel], and [@reeder2023penalized].

## Installation

You can install the development version of SemiCompRisksFreq from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("harrisonreeder/SemiCompRisksFreq")
```

## Example

This is a basic example which shows you how to solve a common problem:

```{r example}
library(SemiCompRisksFreq)
## basic example code

#loading a data set
data(scrData)

#fitting Weibull semi-Markov illness-death model with gamma frailties
form <- Formula::Formula(time1 + event1 | time2 + event2 ~ x1 + x2 + x3 | x1 + x2 | x1 + x2)
fit_WB	<- FreqID_HReg2(Formula = form, data=scrData, model="semi-Markov",
                       extra_starts = 0,hazard = "weibull",frailty = TRUE,optim_method = c("BFGS"))

#exploring results
fit_WB
summ.fit_WB <- summary(fit_WB); names(summ.fit_WB)
summ.fit_WB
pred_WB <- predict(fit_WB, tseq=seq(from=0, to=30, length.out=100))
plot(pred_WB, plot.est="Haz")
plot(pred_WB, plot.est="Surv")

```

